Probabilistic Symbol Encoding for \\Convolutional Associative Memories

### 2017-01-19 papers/hrr-paper/paper.tex
Fix normalization formula
Fix sentence

	In the case of lookup tables, in order to decode a specific symbolic vector, the elements from a symbol table are iterated over, the similarity to each of the entries is calculated and the symbol which presented maximum similarity is returned. With the help of a threshold for the similarity value false-positives can be excluded. A lookup requires $O(n)$, where $n$ is the number of symbols known to the system. This approach works quite well for object identifiers (names), but has some non-desirable properties when used on scalar encoding. The space complexity will increase and may become infeasible, depending on the number of inputs needed. One way of handling symbolic scalar encoding is to discretize the whole input range into bins and assigning a random vector to each discrete value. This however may often prove to not satisfy the task needs any more.
In this paper, we present a probabilistic method for removing the necessity of
using a clean-up procedure after decoding scalar values.

@@

	\begin{equation}
	x_i = x_i - \frac{\sum_{i=0}^n ||x_i||}{|x|}
	\end{equation}

	\begin{equation}
	\pmb x = \frac{\pmb x }{ \| \pmb x \|}
	\end{equation}

>>>>

	In the case of lookup tables, in order to decode a specific symbolic vector, the elements from a symbol table are iterated over, the similarity to each of the entries is calculated and the symbol which presented maximum similarity is returned. With the help of a threshold for the similarity value false-positives can be excluded. A lookup requires $O(n)$, where $n$ is the number of symbols known to the system. This approach works quite well for object identifiers (names), but has some non-desirable properties when used on scalar encoding. The space complexity will increase and may become infeasible, depending on the number of inputs needed. One way of handling symbolic scalar encoding is to discretize the whole input range into bins and assigning a random vector to each discrete value. This, however may often prove to not satisfy the task needs any more.
In this paper, we present an intrinsic, probabilistic encoding and decoding
method, which removes the necessity of using a symbol table.

@@

	\begin{equation}\label{eq:norm1}
		{x_i}' = x_i - \frac{\sum_j x_j}{|{\pmb x}|},
	\end{equation}
and
	\begin{equation}\label{eq:norm2}
		{\pmb x}{'}{'} = \frac{{\pmb x}'}{ \| {\pmb x}'\|},
	\end{equation}
which normalize ${\pmb x}$ to a mean value of $0$ and a length of $1$.
